---
title: "read_chemprop_predictions"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

http://ec2-52-90-145-233.compute-1.amazonaws.com:9100/hub/login


```{r}
library(tidyverse)
library(magrittr)
library(pROC)
library(eulerr)
library(PRROC)
library(ggplot2)
  library(plotROC)
```

# read test data 
```{r}
response_train <- read_csv('../../../analysis/scaffold_based/assay_matrix_discrete_train_old_scaff.csv')  %>% 
  print

values_per_assay_train <- response_train %>% 
  select(-Metadata_broad_sample_simple) %>% 
  summarise_all(funs(sum(!is.na(.)))) %>% 
  as.matrix() %>% 
  t() %>% 
  print

hits_per_assay_train <- response_train %>%
  select(-Metadata_broad_sample_simple) %>% 
  colSums(., na.rm = TRUE) %>% 
  as_tibble() %>% 
  rename(hits = value) %>% 
  mutate(assay_id = colnames(response_train %>% select(-Metadata_broad_sample_simple)), readouts = values_per_assay_train) %>% 
  select(assay_id, readouts, hits) %>%
  mutate(hit_rate = hits/readouts) %>%
  filter(hits > 0) %>%
  arrange(-hits) %>% 
  print

ggplot(hits_per_assay_train, aes(x = hits)) + 
  geom_histogram() + 
  theme_test()

ggplot(hits_per_assay_train, aes(x = hit_rate)) + 
  geom_histogram() + 
  theme_test()

ggplot(hits_per_assay_train, aes(x = hit_rate, y = readouts)) + 
  geom_point() + 
  theme_test()

hits_per_assay_train %>% 
  summarise(mean_hit_rate = mean(hit_rate, na.rm = TRUE))


```

# read test data 
```{r}
response <- read_csv('../../../analysis/scaffold_based/assay_matrix_discrete_test_old_scaff.csv')  %>% 
  print

values_per_assay <- response %>% 
  select(-Metadata_broad_sample_simple) %>% 
  summarise_all(funs(sum(!is.na(.)))) %>% 
  as.matrix() %>% 
  t() %>% 
  print

hits_per_assay <- response %>%
  select(-Metadata_broad_sample_simple) %>% 
  colSums(., na.rm = TRUE) %>% 
  as_tibble() %>% 
  rename(hits = value) %>% 
  mutate(assay_id = colnames(response %>% select(-Metadata_broad_sample_simple)), readouts = values_per_assay) %>% 
  select(assay_id, readouts, hits) %>%
  mutate(hit_rate = hits/readouts) %>%
  filter(hits > 0) %>% 
  arrange(-hits) %>% 
  print

ggplot(hits_per_assay, aes(x = hits)) + 
  geom_histogram() + 
  theme_test()

ggplot(hits_per_assay, aes(x = hit_rate)) + 
  geom_histogram() + 
  theme_test()

ggplot(hits_per_assay, aes(x = hit_rate, y = readouts)) + 
  geom_point() + 
  theme_test()

hits_per_assay %>% 
  summarise(mean_hit_rate = mean(hit_rate))


```

# we read one prediction file to get the test assays
```{r}
one_prediction <- read_csv('../../../results/scaffold_based/chemprop/predictions/predictions_cp_op.csv')
```

# todo 
# 1. class inabalce for each assay 
# 2. tested compounds for each assay


# annoated assay information from bridget 
```{r}
assay_annotation <- read_csv('../../../analysis/201802_pumr_baseline_prediction_177_assays.csv') %>%
  select(ASSAY_PUMA_ID, n_compounds, ASSAY_ID, ASSAY_NAME, OBS_NAME, OBS_SOURCE, ASSAY_TYPE, READOUT_TYPE,candidates) %>% 
  print
```

```{r}
# how many different assay types are available?
unique(assay_annotation$ASSAY_TYPE)

## todo: check entry with obs source 762, the row is invalid 
assay_annotation %>% filter(OBS_SOURCE == 762)
```

```{r}
assay_annotation %>% 
  filter(OBS_SOURCE != 762) %>% 
  group_by(ASSAY_TYPE) %>% 
  summarise(n = n()) %>% 
  arrange(-n)
```

# define helper functions
```{r}
# helper function to catch test data without hits (only 0 or NA values)
auc_with_na <- function(response, result){
  ifelse(
    max(response >0, na.rm = TRUE) == 0,
    return(NA), 
    auc(response, result, direction = "<", levels = c(0, 1))
  )
} 

# TODO
# helper function to catch test data without hits (only 0 or NA values)
prauc_with_na <- function(response, result){
  ifelse(
    max(response >0, na.rm = TRUE) == 0,
    return(NA), 
    pr.curve(response, result, direction = "<", levels = c(0, 1))
  )
} 

# read and evaluate predictions and return results as data frame
evaluate_chemprop <- function(path_prediction) {
  predictions <- read_csv(path_prediction)
  descriptor <- basename(path_prediction) %>% str_sub(13,-5) 
  tibble(
    assay_id = colnames(response[,2:length(response)]),
    auc = mapply(
      auc_with_na, 
      as.list(response[,2:length(response)]), as.list(predictions[,2:length(predictions)]) 
      ),
    descriptor = descriptor
  )
} 

```
The main characteristic of the assay data is
1. sparseness 
2. class inbalance 
# 
```{r}

file_list <- list.files('../../../results/scaffold_based/chemprop/predictions', pattern = "*.csv", full.names = TRUE) %>% 
  print

result <- do.call(rbind, lapply(file_list, evaluate_chemprop)) %>% 
  mutate("auc_70" = auc >0.7) %>% 
  mutate("auc_90" = auc >0.9) 


result %>% 
  group_by(descriptor) %>% 
  summarize(assays_total = n(),
          assays_evaluated = sum(!is.na(auc)),
          assays_not_evaluated = sum(is.na(auc)),
          auc_mean = mean(auc, na.rm = TRUE), 
          auc_70 = sum(auc_70, na.rm = TRUE), 
          auc_90 = sum(auc_90, na.rm = TRUE)
          ) %>% 
  arrange(-auc_mean) %>% 
  #slice(1:20) %>% 
  select(-assays_total, -assays_evaluated,-assays_not_evaluated) %>%
  knitr::kable()

result %>% 
  group_by(descriptor) %>% 
  summarize(assays_total = n(),
          assays_evaluated = sum(!is.na(auc)),
          assays_not_evaluated = sum(is.na(auc)),
          auc_mean = mean(auc, na.rm = TRUE), 
          auc_70 = sum(auc_70, na.rm = TRUE), 
          auc_90 = sum(auc_90, na.rm = TRUE)
          ) %>% 
  arrange(-auc_90) %>% 
  slice(1:5) %>% 
  select(-assays_total, -assays_evaluated,-assays_not_evaluated) %>%
  knitr::kable()

```
merge results with assay annotation 


```{r}
df <- left_join(
  result,
  assay_annotation %>% filter(OBS_SOURCE != 762) %>%  
    select(ASSAY_TYPE, ASSAY_PUMA_ID) %>%
    rename(assay_id = ASSAY_PUMA_ID),
  by = c("assay_id")
  
) %>% 
  print

```

```{r}
df %>% 
  filter(!is.na(ASSAY_TYPE)) %>% 
  group_by(descriptor, ASSAY_TYPE) %>% 
  filter(!is.na(auc)) %>% 
  summarise(n = n(),mean_auc = mean(auc),  percentage_auc90 = mean(auc_90),  percentage_auc70 = mean(auc_70)) %>% 
  write_csv("../../../results/2020-07-results-by-descriptor.csv")
```


```{r}
df %>% 
  filter(!is.na(ASSAY_TYPE)) %>%
  filter(ASSAY_TYPE == "bacterial") %>% 
  group_by(descriptor, ASSAY_TYPE) %>% 
  filter(!is.na(auc)) %>% 
  summarise(n = n(),mean_auc = mean(auc), n_auc_90 = sum(auc_90), percentage_auc90 = mean(auc_90),  percentage_auc70 = mean(auc_70)) %>%
  arrange(-percentage_auc90)
  print

```

```{r}
result %>% 
  group_by(descriptor) %>% 
  filter(!is.na(auc)) %>% 
  summarise(n = n(),mean_auc = mean(auc), n_auc_90 = sum(auc_90), percentage_auc90 = mean(auc_90),  percentage_auc70 = mean(auc_70)) %>%
  arrange(-percentage_auc90) %>% 
  print
```

```{r}

result %<>% left_join(., hits_per_assay, by = "assay_id")

result %>% 
  filter(descriptor %in% c("cp_op_es","mo_op_es","ge_op_es","mo_cp_op_es","ge_mo_cp_op_es")) %>% 
  group_by(descriptor) %>% 
  filter(hits>40) %>% 
  arrange(-auc) %>% 
  slice(1:2)

```

```{r}
ggplot(
  result %>% 
    filter(descriptor %in% c("cp_op_es","mo_op_es","ge_op_es","mo_cp_op_es","ge_mo_cp_op_es")), 
  aes(x = readouts, y = auc, color = descriptor) 
  ) + 
  geom_point() + 
   facet_grid(. ~ descriptor ) 
  #coord_equal()
```


```{r}
result %>% 
  filter(descriptor %in% c("cp_op_es","mo_op_es","ge_op_es","mo_cp_op_es","ge_mo_cp_op_es")) %>% 
  filter(assay_id == "280_759") %>% 
  print
```
```{r}
result %>% 
  filter(descriptor %in% c("cp_op_es","mo_op_es","ge_op_es","mo_cp_op_es","ge_mo_cp_op_es")) %>% 
  filter(assay_id == "282_761") %>% 
  arrange(-auc) %>% 
  print
```

# create auc plots 
```{r}
# read results  mo_cp_op_es pons

result_vector <-  read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_ge_op_es.csv") %>% 
  extract2("282_761") 

response_vector <- response %>% extract2("282_761") 


roc_curve <- roc(response_vector, result_vector,  , direction = "<", levels = c(0, 1)) 

plot(roc_curve)
```

# color codes 
# yellow F1C232 (chemical)
# blue 6FA8DC (gene expression) 
# green 93C47C (morphology)

```{r}
assay_id_to_plot <- "280_759"
assay_id_to_plot <- "241_715"
assay_id_to_plot <- "282_761"
assay_id_to_plot <- "261_739"


result_vector_cp <-  read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_cp_op_es.csv")  
result_vector_mo <-  read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_mo_op_es.csv")  
result_vector_ge <-  read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_ge_op_es.csv") 
 
test_data <- data.frame(
  response =  response %>% extract2(assay_id_to_plot), 
  result_cp = result_vector_cp %>% extract2(assay_id_to_plot),
  result_mo = result_vector_mo %>% extract2(assay_id_to_plot),
  result_ge = result_vector_ge %>% extract2(assay_id_to_plot)
  )


longdata <- melt_roc(test_data, "response", c("result_cp", "result_mo","result_ge"))

ggplot(longdata, aes(d = D, m = M, color = name)) + 
  geom_roc(labels = FALSE, pointsize = 0) + 
  theme_linedraw() + 
  coord_fixed() +
  scale_color_manual(values=c("#F1C232","#6FA8DC","#93C47C")) + 
  ggtitle( paste0("roc_",assay_id_to_plot,".png")   ) + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
    panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
  theme(text = element_text(size=16)) + 
  xlab("False Positive Fraction") +
  ylab("True Positive Fraction")  + 
  theme(legend.position="none")

save_name <- paste0("roc_singe_descriptor_",assay_id_to_plot,".png")
ggsave(paste0("../../../analysis/scaffold_based/",save_name))

```


```{r}
assay_id_to_plot <- "280_759"
assay_id_to_plot <- "241_715"
assay_id_to_plot <- "282_761"
assay_id_to_plot <- "261_739"

result_vector_ge_cp <-  read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_ge_cp_op_es.csv")  
result_vector_ge_mo_cp <-  read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_ge_mo_cp_op_es.csv")  
result_vector_mo_cp <-  read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_mo_cp_op_es.csv") 
result_vector_ge_mo <-  read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_ge_mo.csv") 
 
test_data <- data.frame(
  response =  response %>% extract2(assay_id_to_plot), 
  result_ge_cp = result_vector_ge_cp %>% extract2(assay_id_to_plot),
  result_ge_mo_cp = result_vector_ge_mo_cp %>% extract2(assay_id_to_plot),
  result_mo_cp = result_vector_mo_cp %>% extract2(assay_id_to_plot),
  result_ge_mo = result_vector_ge_mo %>% extract2(assay_id_to_plot)
  )


longdata <- melt_roc(test_data, "response", c("result_ge_cp", "result_ge_mo_cp","result_mo_cp","result_ge_mo"))

ggplot(longdata, aes(d = D, m = M, color = name)) + 
  geom_roc(labels = FALSE, pointsize = 0) + 
  theme_linedraw() + 
  coord_fixed() +
  ggtitle( paste0("roc_",assay_id_to_plot,".png")   ) + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
    panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
  theme(text = element_text(size=16)) + 
  xlab("False Positive Fraction") +
  ylab("True Positive Fraction") 
save_name <- paste0("roc_",assay_id_to_plot,".png")
ggsave(paste0("../../../analysis/scaffold_based/",save_name))

```


```{r}
type <- "mo"

if (type == "cp") { result_vector <-  read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_cp_op_es.csv") } 
if (type == "mo") { result_vector <-  read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_mo_op_es.csv") } 
if (type == "ge") { result_vector <-  read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_ge_op_es.csv") } 
if (type == "cp+mo") { result_vector <-  read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_mo_cp_op_es.csv") } 
if (type == "cp+ge+mo") { result_vector <-  read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_ge_mo_cp_op_es.csv") } 

result_vector

test <- data.frame(
  response =  response %>% extract2(assay_id_to_plot), 
  result = result_vector %>% extract2(assay_id_to_plot)
)

ggplot(test, aes(m = result, d = response)) + 
  geom_roc(labels = FALSE) + 
  theme_linedraw() + 
  coord_fixed() +
  ggtitle(paste0(type, ", auc: ", sprintf("%.3f", auc(test$response, test$result)))) + 
   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
  theme(text = element_text(size=20))

ggsave(paste0("../../../analysis/scaffold_based/",save_name), width = 4, height = 4)

plot(sort(test$result, decreasing = TRUE),xlab = "compound",ylab = "predicted value", main = type)

png(filename=paste0("../../../analysis/scaffold_based/predicted_values_",type,"_",assay_id_to_plot,"_", sprintf("%.3f", auc(test$response, test$result)),".png"),width = 480, height = 480, units = "px", pointsize = 12,)
plot(sort(test$result, decreasing = TRUE),xlab = "compound",ylab = "predicted value", main = type)

dev.off()
```
```{r}

```


# Add columns for ensemble models (true/false) and for optimized models (true/false)
1. Ensemble models end with _es 
2. optimized models have an _op in the filename. 
All ensemble models ending with op_es were created as follows: hyperparmaeter optimization was run using 20 models. The optimal configuration was used to train one final model. This final model and all 20 other models were used in an ensemble model (21 models together) to predict the final results. 

```{r}

is_ensemble <- function(descriptor){
   !is_empty(str_subset(descriptor,"_es"))
}

is_optimized <- function(descriptor){
   !is_empty(str_subset(descriptor,"_op"))
}

result_annotated <- result %>% 
  group_by(descriptor) %>% 
  summarize(assays_total = n(),
          assays_evaluated = sum(!is.na(auc)),
          assays_not_evaluated = sum(is.na(auc)),
          auc_mean = mean(auc, na.rm = TRUE), 
          auc_70 = sum(auc_70, na.rm = TRUE), 
          auc_90 = sum(auc_90, na.rm = TRUE)
          )
result_annotated %<>% 
  mutate(ensemble = unlist(lapply(result_annotated$descriptor, is_ensemble))) %>% 
  mutate(optimized = unlist(lapply(result_annotated$descriptor, is_optimized))) %>% 
  select(descriptor, optimized, ensemble, everything()) %>% 
  print

```
* 14 assays have a auc>90 for all three descriptors 
* 31 assays have a auc>90 for two descriptors 
* 49 assays have a auc>90 for one descriptor
```{r}
result %>% 
  filter(auc_90) %>% 
  group_by(assay_id) %>% 
  summarise(descriptors_with_auc90 = n()) %>% 
  group_by(descriptors_with_auc90) %>% 
  summarise(n_assay = n()) %>% 
  arrange(n_assay) %>% 
  print
```

## how did optimization improve our model?
```{r}
 descriptor_list <- c("cp","ge","mo","mo_cp","ge_cp","ge_mo_cp")

improvement_op_auc_mean <- function(string) {
  return( 
    result_annotated %>% filter( descriptor == paste0(string,"_op")) %>% extract2("auc_mean") / 
      result_annotated %>% filter( descriptor == paste0(string)) %>% extract2("auc_mean")
  )
}

improvement_es_auc_mean <- function(string) {
  return( 
    result_annotated %>% filter( descriptor == paste0(string,"_op_es")) %>% extract2("auc_mean") / 
      result_annotated %>% filter( descriptor == paste0(string)) %>% extract2("auc_mean")
  )
}

improvement_op_auc_90 <- function(string) {
  return( 
    result_annotated %>% filter( descriptor == paste0(string,"_op")) %>% extract2("auc_90") / 
      result_annotated %>% filter( descriptor == paste0(string)) %>% extract2("auc_90")
  )
}

improvement_es_auc_90 <- function(string) {
  return( 
    result_annotated %>% filter( descriptor == paste0(string,"_op_es")) %>% extract2("auc_90") / 
      result_annotated %>% filter( descriptor == paste0(string)) %>% extract2("auc_90")
  )
}

improvement_df <- tibble(
  descriptor = descriptor_list,
  impr_auc_90_opti = lapply(descriptor_list, improvement_op_auc_90) %>% unlist(), 
  impr_auc_90_ensemble =  lapply(descriptor_list, improvement_es_auc_90) %>% unlist(),
  impr_auc_mean_opti = lapply(descriptor_list, improvement_op_auc_mean) %>% unlist(), 
  impr_auc_mean_ensemble =  lapply(descriptor_list, improvement_es_auc_mean) %>% unlist()
) %>% 
  print
  
```


 c("cp_op_es","mo_op_es","ge_op_es","mo_cp_op_es","ge_mo_cp_op_es","ge_mo","ge_cp_op_es")) 
```{r}
result %>% 
  filter(descriptor %in% c("cp_op_es","mo_op_es","ge_op_es")) %>% 
  mutate(descriptor=replace(descriptor, descriptor=="cp_op_es", "CP")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_op_es", "GE")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="mo_op_es", "MO")) %>%
  mutate(auc_70 = ifelse(is.na(auc_70),FALSE, auc_70)) %>% 
  select(assay_id, descriptor, auc_70) %>% 
  spread(.,descriptor, auc_70) %>% 
  select(-assay_id) %>% 
  euler(.) %>% 
  plot(
    .,
    quantities = TRUE, 
    main = "Assays with auc > 0.7 per descriptor",
    fills = c("#F1C232","#6FA8DC","#93C47C")
                ) 
```

```{r}
result %>% 
  filter(descriptor %in% c("cp_op_es","mo_op_es","ge_op_es")) %>% 
  mutate(descriptor=replace(descriptor, descriptor=="cp_op_es", "CP")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_op_es", "GE")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="mo_op_es", "MO")) %>%
  mutate(auc_90 = ifelse(is.na(auc_90),FALSE, auc_90)) %>% 
  select(assay_id, descriptor, auc_90) %>% 
  spread(.,descriptor, auc_90) %>% 
  select(-assay_id) %>% 
  euler(.) %>% 
  plot(
    .,
    quantities = TRUE, 
    main = "Assays with auc > 0.9 per descriptor",
    fills = c("#F1C232","#6FA8DC","#93C47C")
                ) 
```
 c("cp_op_es","mo_op_es","ge_op_es","mo_cp_op_es","ge_mo_cp_op_es","ge_mo","ge_cp_op_es")) 
 
```{r}
result %>% 
  filter(descriptor %in% c("mo_cp_op_es","ge_mo_cp_op_es","ge_mo","ge_cp_op_es")) %>% 
  mutate(descriptor=replace(descriptor, descriptor=="mo_cp_op_es", "CP+MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_mo_cp_op_es", "CP+GE+MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_mo", "GE+MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_cp_op_es", "CP+GE")) %>%
  mutate(auc_70 = ifelse(is.na(auc_70),FALSE, auc_70)) %>% 
  select(assay_id, descriptor, auc_70) %>% 
  spread(.,descriptor, auc_70) %>% 
  select(-assay_id) %>% 
  euler(.) %>% 
  plot(.,
       quantities = TRUE, 
       main = "Assays with auc > 0.7 per descriptor",
       fills = c("#F8766D", "#7CAE00", "#00BFC4","#C77CFF"),
       edges = TRUE
       ) 
```


```{r}
result %>% 
  filter(descriptor %in% c("mo_cp_op_es","ge_mo_cp_op_es","ge_mo","ge_cp_op_es")) %>% 
  mutate(descriptor=replace(descriptor, descriptor=="mo_cp_op_es", "CP+MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_mo_cp_op_es", "CP+GE+MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_mo", "GE+MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_cp_op_es", "CP+GE")) %>%
  mutate(auc_90 = ifelse(is.na(auc_90),FALSE, auc_90)) %>% 
  select(assay_id, descriptor, auc_90) %>% 
  spread(.,descriptor, auc_90) %>% 
  select(-assay_id) %>% 
  euler(.) %>% 
  plot(.,
       quantities = TRUE, 
       main = "Assays with auc > 0.9 per descriptor",
       fills = c("#F8766D", "#7CAE00", "#00BFC4","#C77CFF"),
       edges = TRUE
       ) 
```


# not used 
```{}
result %>% 
  filter(descriptor %in% c("mo_cp","ge_cp","ge_mo_cp")) %>% 
  mutate(auc_90 = ifelse(is.na(auc_90),FALSE, auc_90)) %>% 
  select(assay_id, descriptor, auc_90) %>% 
  spread(.,descriptor, auc_90) %>% 
  select(-assay_id) %>% 
  euler(.) %>% 
  plot(.,quantities = TRUE, main = "Assays with auc > 0.9 per descriptor") 

result %>% 
  filter(descriptor %in% c("mo_cp_op_es","mo_op_es","mo_op")) %>% 
  mutate(auc_90 = ifelse(is.na(auc_90),FALSE, auc_90)) %>% 
  select(assay_id, descriptor, auc_90) %>% 
  spread(.,descriptor, auc_90) %>% 
  select(-assay_id) %>% 
  euler(.) %>% 
  plot(.,quantities = TRUE, main = "Assays with auc > 0.9 per descriptor") 

result %>% 
  filter(descriptor %in% c("mo_cp","ge_cp","ge_mo_cp")) %>% 
  mutate(auc_90 = ifelse(is.na(auc_90),FALSE, auc_90)) %>% 
  select(assay_id, descriptor, auc_90) %>% 
  spread(.,descriptor, auc_90) %>% 
  select(-assay_id) %>% 
  euler(.) %>% 
  plot(.,quantities = TRUE, main = "Assays with auc > 0.9 per descriptor") 

result %>% 
  filter(descriptor %in% c("mo","mo_2","mo_3")) %>% 
  mutate(auc_90 = ifelse(is.na(auc_90),FALSE, auc_90)) %>% 
  select(assay_id, descriptor, auc_90) %>% 
  spread(.,descriptor, auc_90) %>% 
  select(-assay_id) %>% 
  colSums() %>%
  euler(.) %>% 
  plot(.,quantities = TRUE, main = "Assays with auc > 0.9 per descriptor") 
```

# the following code can only be run with access to the assay_metadata.csv
## assay distribution




# read assay information 
```{}
assay_info <- read_csv('../../../analysis/assay_metadata.csv') %>% 
  group_by(ASSAY_ID, ASSAY_OBS_ID) %>% 
  slice(1) 

assay_info %<>% 
  mutate(new_id = paste0(ASSAY_ID,"_", ASSAY_OBS_ID)) %>% print
```

```{}
assay_info %>% 
  group_by(OBS_SOURCE) %>% 
  summarise(assays_per_source = n())

assay_info %<>% 
  select(-starts_with("assays_per_")) %>% 
  left_join(
    x = .,
    y = assay_info %>% 
      group_by(OBS_SOURCE) %>% 
      summarise(assays_per_source = n()),
    by = "OBS_SOURCE"
  )

```

```{}
summary_per_source <- left_join(
  x = result %>% filter(auc_90),
  y = assay_info, 
  by = c("assay_id" = "new_id")
) %>% 
  group_by(descriptor, OBS_SOURCE ) %>% 
  summarise( auc90_n = n())  %>% 
  print
```
```{}
summary_per_source %>% left_join(
  x = ., 
  y = assay_info %>% 
      group_by(OBS_SOURCE) %>% 
      summarise(assays_per_source = n()),
    by = "OBS_SOURCE"
)  %>% 
  mutate(auc90_percent_per_source = auc90_n / assays_per_source) %>% 
  select(descriptor, OBS_SOURCE, auc90_n, assays_per_source, auc90_percent_per_source, ) %>% 
  knitr::kable()

```

# legacy - the following code can be used to parse the command line output of train.py if --show_individual_scores is set 

```{}
read_chemprop_results <- function(result_path){ 
  read_delim(result_path, delim = " ", col_names = FALSE) %>% 
    select(X3, X6) %>% 
    rename("assay_id" = X3, "auc" = X6) %>% 
    mutate("auc_70" = auc >0.7) %>% 
    mutate("auc_90" = auc >0.9) %>% 
      return()
}

chemprop_results <- rbind(
  read_chemprop_results('../../../results/scaffold_based_chemprop/results_chemprop.txt') %>% 
    mutate(descriptor = "cp"),
  read_chemprop_results('../../../results/scaffold_based_chemprop/results_chemprop_mo.txt') %>% 
    mutate(descriptor = "cp-mo"),
  read_chemprop_results('../../../results/scaffold_based_chemprop/results_chemprop_ge.txt') %>% 
    mutate(descriptor = "cp-ge"),
  read_chemprop_results('../../../results/scaffold_based_chemprop/results_chemprop_gemo.txt') %>% 
    mutate(descriptor = "cp-ge-mo")
)
 
```


```{r}
result %>% 
  filter(descriptor == "mo") %>%
  group_by(descriptor) %>% 
  arrange(-auc) %>% 
  print

assays_used_in_roc <- result %>% 
  filter(assay_id %in% c("280_759","241_715","282_761","261_739")) %>% 
  filter(descriptor %in% c("cp_op_es","mo_op_es","ge_op_es","mo_cp_op_es","ge_mo_cp_op_es","ge_mo","ge_cp_op_es")) %>% 
  select(assay_id, auc, descriptor,hits, readouts, hit_rate) %>% 
  print
```


```{r}
count_auc_70_by_assay_type <- df %>% 
  filter(descriptor %in% c("cp_op_es","mo_op_es","ge_op_es","mo_cp_op_es","ge_mo_cp_op_es","ge_mo","ge_cp_op_es")) %>% 
  mutate(descriptor=replace(descriptor, descriptor=="cp_op_es", "CP")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_op_es", "GE")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="mo_op_es", "MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="mo_cp_op_es", "CP+MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_mo_cp_op_es", "CP+GE+MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_mo", "GE+MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_cp_op_es", "CP+GE")) %>%
  filter(auc_70) %>% 
  group_by(descriptor,ASSAY_TYPE) %>% 
  summarise(n_auc_70 = n()) %>% 
  filter(!is.na(ASSAY_TYPE)) %>% 
  print
```
```{r}
count_auc_70_by_descriptor_and_type <- pivot_wider(
  count_auc_70_by_assay_type,  
  names_from = ASSAY_TYPE,
  values_from = n_auc_70
  ) %>% print


```


```{r}
count_auc_90_by_assay_type <- df %>% 
  filter(descriptor %in% c("cp_op_es","mo_op_es","ge_op_es","mo_cp_op_es","ge_mo_cp_op_es","ge_mo","ge_cp_op_es")) %>% 
  mutate(descriptor=replace(descriptor, descriptor=="cp_op_es", "CP")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_op_es", "GE")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="mo_op_es", "MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="mo_cp_op_es", "CP+MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_mo_cp_op_es", "CP+GE+MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_mo", "GE+MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_cp_op_es", "CP+GE")) %>%
  filter(auc_90) %>% 
  group_by(descriptor,ASSAY_TYPE) %>% 
  summarise(n_auc_90 = n()) %>% 
  filter(!is.na(ASSAY_TYPE)) 

count_auc_90_by_descriptor_and_type <- pivot_wider(
  count_auc_90_by_assay_type,  
  names_from = ASSAY_TYPE,
  values_from = n_auc_90
  ) %>% print

```

```{r}
result_auc_summary <- result %>% 
  filter(descriptor %in% c("cp_op_es","mo_op_es","ge_op_es","mo_cp_op_es","ge_mo_cp_op_es","ge_mo","ge_cp_op_es")) %>% 
  mutate(descriptor=replace(descriptor, descriptor=="cp_op_es", "CP")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_op_es", "GE")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="mo_op_es", "MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="mo_cp_op_es", "CP+MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_mo_cp_op_es", "CP+GE+MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_mo", "GE+MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_cp_op_es", "CP+GE")) %>%
  group_by(descriptor) %>% 
  summarise(
    "Mean AUC" = mean(auc, na.rm = TRUE), 
    "AUC > 0.7" = sum(auc_70, na.rm = TRUE),
    "AUC > 0.9" = sum(auc_90, na.rm = TRUE)
    )


result %>% arrange(-auc) %>% 
  filter(descriptor %in% c("cp_op_es","mo_op_es","ge_op_es","mo_cp_op_es","ge_mo_cp_op_es","ge_mo","ge_cp_op_es")) %>% 
  mutate(descriptor=replace(descriptor, descriptor=="cp_op_es", "CP")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_op_es", "GE")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="mo_op_es", "MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="mo_cp_op_es", "CP+MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_mo_cp_op_es", "CP+GE+MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_mo", "GE+MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_cp_op_es", "CP+GE")) %>%
  select(assay_id, auc, descriptor, hits, everything()) %>% 
  filter(!is.na(readouts) ) %>% 
  write_csv("~/tmp.csv")

df_temp <- result %>% arrange(-auc) %>% 
  filter(descriptor %in% c("cp_op_es","mo_op_es","ge_op_es","mo_cp_op_es","ge_mo_cp_op_es","ge_mo","ge_cp_op_es")) %>% 
  mutate(descriptor=replace(descriptor, descriptor=="cp_op_es", "CP")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_op_es", "GE")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="mo_op_es", "MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="mo_cp_op_es", "CP+MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_mo_cp_op_es", "CP+GE+MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_mo", "GE+MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_cp_op_es", "CP+GE")) %>%
  select(assay_id, auc, descriptor, hits, everything()) %>% 
  group_by(assay_id) %>% 
  summarise(mean_auc = mean(auc), hits = mean(hits), readouts = mean(readouts), hit_rate = mean(hit_rate)) %>% 
  filter(!is.na(readouts) ) %>% 
  print


```
