---
title: "Evaluate assay prediction baseded on chemical, genetic and morphological description "
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

http://ec2-52-90-145-233.compute-1.amazonaws.com:9100/hub/login

Used input files: 
response_train <- read_csv('../../../analysis/scaffold_based/assay_matrix_discrete_train_old_scaff.csv')  
response <- read_csv('../../../analysis/scaffold_based/assay_matrix_discrete_test_old_scaff.csv')  
assay_annotation <- read_csv('../../../analysis/201802_pumr_baseline_prediction_177_assays.csv')
file_list <- list.files('../../../results/scaffold_based/chemprop/predictions', pattern = "*.csv", full.names = TRUE) 

Output files / created files : 
result_annotated %>% write_csv("../../../results/scaffold_based/chemprop/2020_07_evaluation_all_data.csv")
result_analyzed %>% write_csv("../../../results/scaffold_based/chemprop/2020_07_evaluation.csv")

This notebook is used to create the initial evaluation for the data in this study. 

Notebooks that use the results
* VennDiagramm 

Tables created in this notebook:
* distribution of assay type 


```{r}
library(tidyverse)
library(magrittr)
library(ggplot2)
library(pROC)
```
# Statistics of the training data set 
For each assay we calculate 
1. total number of readouts/compounds 
2. hits  
3. hitrate 
```{r}
response_train <- read.csv('../predictions/assay_matrix_discrete_train_old_scaff.csv', check.names = F)

values_per_assay_train <- response_train %>% 
  select(-Metadata_broad_sample_simple) %>% 
  summarise_all(funs(sum(!is.na(.)))) %>% 
  as.matrix() %>% 
  t() %>% 
  print

hits_per_assay_train <- response_train %>%
  select(-Metadata_broad_sample_simple) %>% 
  colSums(., na.rm = TRUE) %>% 
  as_tibble() %>% 
  rename(hits = value) %>% 
  mutate(assay_id = colnames(response_train %>% select(-Metadata_broad_sample_simple)), readouts = values_per_assay_train) %>% 
  select(assay_id, readouts, hits) %>%
  mutate(hit_rate = hits/readouts) %>%
  filter(hits > 0) %>%
  arrange(-hits) %>% 
  print

ggplot(hits_per_assay_train, aes(x = hits)) + 
  geom_histogram() + 
  theme_test()

ggplot(hits_per_assay_train, aes(x = hit_rate)) + 
  geom_histogram() + 
  theme_test()

ggplot(hits_per_assay_train, aes(x = hit_rate, y = readouts)) + 
  geom_point() + 
  theme_test()

hits_per_assay_train %>% 
  summarise(mean_hit_rate = mean(hit_rate, na.rm = TRUE))
```

```{}
df <- left_join( 
  result,
  hits_per_assay_train %>% 
  rename("hits_train" = hits)  %>% 
  rename("readouts_train" = readouts)  %>% 
  rename("hit_rate_train" = hit_rate),
  by = "assay_id"
) 

ggplot(data = df, aes(x = readouts_train, y = auc)) + 
  geom_point() +
  geom_smooth()

ggplot(data = df, aes(x = hits_train, y = auc)) + 
  geom_point() +
  geom_smooth()
  
ggplot(data = df, aes(x = hit_rate_train, y = auc, color = ASSAY_TYPE)) + 
  geom_point() +
  geom_smooth(alpha = .2)
  

```

# Statistics of the test data set 
For each assay we calculate 
1. total number of readouts/compounds 
2. hits  
3. hitrate 
```{r}
# response <- read_csv('../../../analysis/scaffold_based/assay_matrix_discrete_test_old_scaff.csv')
response <- read.csv('../predictions/assay_matrix_discrete_test_old_scaff.csv', check.names = F)  

values_per_assay <- response %>% 
  select(-Metadata_broad_sample_simple) %>% 
  summarise_all(funs(sum(!is.na(.)))) %>% 
  as.matrix() %>% 
  t() %>% 
  print

hits_per_assay <- response %>%
  select(-Metadata_broad_sample_simple) %>% 
  colSums(., na.rm = TRUE) %>% 
  as_tibble() %>% 
  rename(hits = value) %>% 
  mutate(assay_id = colnames(response %>% select(-Metadata_broad_sample_simple)), readouts = values_per_assay) %>% 
  select(assay_id, readouts, hits) %>%
  mutate(hit_rate = hits/readouts) %>%
  filter(hits > 0) %>% 
  arrange(-hits) %>% 
  print

ggplot(hits_per_assay, aes(x = hits)) + 
  geom_histogram() + 
  theme_test()

ggplot(hits_per_assay, aes(x = hit_rate)) + 
  geom_histogram() + 
  theme_test()

ggplot(hits_per_assay, aes(x = hit_rate, y = readouts)) + 
  geom_point() + 
  theme_test()

hits_per_assay %>% 
  summarise(mean_hit_rate = mean(hit_rate))
```

# Read manually annotated assay information
For some assays the assay type was manually labeled
```{r}
#assay_annotation <- read_csv('../../../analysis/201802_pumr_baseline_prediction_177_assays.csv') %>%
assay_annotation <- read_csv('../data/201802_pumr_baseline_prediction_177_assays.csv') %>%
  select(ASSAY_PUMA_ID, n_compounds, ASSAY_ID, ASSAY_NAME, OBS_NAME, OBS_SOURCE, ASSAY_TYPE, READOUT_TYPE,candidates) 

# how many different assay types are available?
unique(assay_annotation$ASSAY_TYPE)

## todo: check entry with obs source 762, the row is invalid 
assay_annotation %>% filter(OBS_SOURCE == 762)
```
# remove the wrongly annotated entry with OBS_SOURCE 762
```{r}
assay_annotation %<>% filter(OBS_SOURCE != 762)
```

# Assay count by assay source
```{r}
assay_annotation %>% 
  group_by(ASSAY_TYPE) %>% 
  summarise(n = n()) %>% 
  arrange(-n)
```
```{r}
assay_annotation_summary <- assay_annotation %>% 
  group_by(ASSAY_TYPE) %>% 
  summarise(n = n()) %>% 
  arrange(ASSAY_TYPE)  %>% 
  print

assay_annotation_summary %<>%
  mutate( percentage = n / sum(assay_annotation_summary$n) ) %>% 
  mutate( percentage_text = paste0(round(1000 * percentage) /10,"%") ) %>% 
  select(ASSAY_TYPE, n , percentage_text, percentage) %>% 
  print
```

```{r}
ggplot(data = assay_annotation_summary,  aes(x="", y=n, fill=ASSAY_TYPE)) +
  geom_bar(width = 1, stat = "identity") + 
  geom_text(aes(x=1.6,label = percentage_text), size = 4,position = position_stack(vjust = 0.5))+ 
  coord_polar("y", start=0) + 
  theme_void()+ 
  scale_fill_brewer(palette = "RdBu") 
```

# Evaluate assays  

## define helper functions for evaluation 
The results are stored separately for each predictor and sequetially read, evluated and all resuls are merged into one data frame. 
```{r}
# helper function to catch test data without hits (only 0 or NA values)
auc_with_na <- function(response, result){
  ifelse(
    all(is.na(response)) | max(response >0, na.rm = TRUE) == 0 | max(response <1, na.rm = TRUE) == 0,
    return(NA), 
    auc(response, result, direction = "<", levels = c(0, 1))
  )
} 

# read and evaluate predictions and return results as data frame
evaluate_chemprop <- function(path_prediction) {
  predictions <- read_csv(path_prediction)
  descriptor <- basename(path_prediction) %>% str_sub(13,-5) 
  tibble(
    assay_id = colnames(response[,2:length(response)]),
    auc = mapply(
      auc_with_na, 
      as.list(response[,2:length(response)]), as.list(predictions[,2:length(predictions)]) 
      ),
    descriptor = descriptor
  )
}
  
```


## sequentially read and evaluate predictions 
```{r}
#file_list <- list.files('../../../results/scaffold_based/chemprop/predictions', pattern = "*.csv", full.names = TRUE)
file_list <- list.files('../predictions/predictions/', pattern = "*.csv", full.names = TRUE) 

result <- do.call(rbind, lapply(file_list, evaluate_chemprop)) %>% 
  mutate("auc_70" = round(auc, 12) >0.7) %>% 
  mutate("auc_90" = round(auc, 12) >0.9) 

```

## add readout count, number of hits and hit rate 
```{r} 
result %<>% left_join(., hits_per_assay, by = "assay_id")
```

## add manual annotations
```{r}
result_annotated <- left_join(
  result,
  assay_annotation %>% filter(OBS_SOURCE != 762) %>%  
    select(ASSAY_TYPE, ASSAY_PUMA_ID) %>%
    rename(assay_id = ASSAY_PUMA_ID),
  by = c("assay_id")
  
) %>% 
  print
```

## Create data frame containing all assay information used for analysis
Descriptors will be renamed and filtered. 

Details: For some descriptors we calculated several predictors. We only keep predictors with 
hyperparameter optimized ensemble model (these descriptors end with 'op_es'). The only 
excemption is the predictor using genetic and morphological information. 
```{r}
result_analyzed <- result_annotated %>% 
  filter(descriptor %in%  c("cp_op_es","mo_op_es","ge_op_es","mo_cp_op_es","ge_mo_cp_op_es","ge_mo","ge_cp_op_es")) %>% 
  mutate(descriptor=replace(descriptor, descriptor=="mo_cp_op_es", "CS+MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_mo_cp_op_es", "CS+GE+MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_mo", "GE+MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_cp_op_es", "CS+GE")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="mo_op_es", "MO")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="ge_op_es", "GE")) %>%
  mutate(descriptor=replace(descriptor, descriptor=="cp_op_es", "CS")) 
```


## write all assays as csv 
```{r}
result_annotated$auc <- round(result_annotated$auc, digits = 12)
# all results 
# result_annotated %>% write_csv("../../../results/scaffold_based/chemprop/2020_07_evaluation_all_data.csv")
result_annotated %>% write_csv("../predictions/2021_03_evaluation_all_data.csv")
# results relevant  for analysis
# result_analyzed %>% write_csv("../../../results/scaffold_based/chemprop/2020_07_evaluation.csv")
result_analyzed %>% write_csv("../predictions/2021_03_evaluation.csv")
```
## Summary of predictor using AUC
```{r}
result %>% 
  group_by(descriptor) %>% 
  summarize(assays_total = n(),
          assays_evaluated = sum(!is.na(auc)),
          assays_not_evaluated = sum(is.na(auc)),
          auc_mean = mean(auc, na.rm = TRUE),
          auc_70 = sum(auc_70, na.rm = TRUE), 
          auc_90 = sum(auc_90, na.rm = TRUE)
          ) %>% 
  arrange(-auc_mean) %>% 
  select(-assays_total, -assays_evaluated,-assays_not_evaluated) %>%
  knitr::kable()
``` 
