---
title: "read_chemprop_predictions"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

http://ec2-52-90-145-233.compute-1.amazonaws.com:9100/hub/login

##Input 
response <- read_csv('../../../analysis/scaffold_based/assay_matrix_discrete_test_old_scaff.csv')

result_vector_cp <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_cp_op_es.csv")  
result_vector_mo <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_mo_op_es.csv")  
result_vector_ge <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_ge_op_es.csv") 
result_vector_ge_cp <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_ge_cp_op_es.csv")  
result_vector_mo_cp <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_mo_cp_op_es.csv") 
result_vector_ge_mo <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_ge_mo.csv") 
result_vector_ge_mo_cp <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_ge_mo_cp_op_es.csv") 

## Optional output: 
  save_name <- paste0("roc_singe_descriptor_",assay_id_to_plot,".png")
  ggsave(paste0("../../../analysis/scaffold_based/",save_name))

## colors 
The color map sucks. To change it, use the line 
``` scale_color_manual(values=c("#F1C232","#6FA8DC","#93C47C")) ```
 in each plot function

```{r}
library(tidyverse)
library(magrittr)
library(ggplot2)
library(plotROC)
library(pROC)
```
# read test data 
```{r}
response <- read_csv('../../../analysis/scaffold_based/assay_matrix_discrete_test_old_scaff.csv')  %>% 
  print
```
## read assay prediction
```{r}
result_vector_cp <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_cp_op_es.csv")  
result_vector_mo <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_mo_op_es.csv")  
result_vector_ge <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_ge_op_es.csv") 
result_vector_ge_cp <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_ge_cp_op_es.csv")  
result_vector_mo_cp <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_mo_cp_op_es.csv") 
result_vector_ge_mo <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_ge_mo.csv") 
result_vector_ge_mo_cp <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_ge_mo_cp_op_es.csv")  
```
# color codes 
# yellow F1C232 (chemical)
# blue 6FA8DC (gene expression) 
# green 93C47C (morphology)

```{r}

plot_roc_single_predictors <- function(assay_id_to_plot) {
 
  test_data <- data.frame(
    response =  response %>% extract2(assay_id_to_plot), 
    result_cp = result_vector_cp %>% extract2(assay_id_to_plot),
    result_mo = result_vector_mo %>% extract2(assay_id_to_plot),
    result_ge = result_vector_ge %>% extract2(assay_id_to_plot)
    )
  
  longdata <- melt_roc(test_data, "response", c("result_cp", "result_mo","result_ge"))
  
  ggplot(longdata, aes(d = D, m = M, color = name)) + 
    geom_roc(labels = FALSE, pointsize = 0) + 
    theme_linedraw() + 
    coord_fixed() +
    scale_color_manual(values=c("#F1C232","#6FA8DC","#93C47C")) + 
    ggtitle( paste0("roc_",assay_id_to_plot,".png")   ) + 
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
      panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
    theme(text = element_text(size=16)) + 
    xlab("False Positive Fraction") +
    ylab("True Positive Fraction")  + 
    theme(legend.position="none")
  
  #save_name <- paste0("roc_singe_descriptor_",assay_id_to_plot,".png")
  #ggsave(paste0("../../../analysis/scaffold_based/figures/",save_name))
}
```

```{r}
plot_roc_single_predictors("280_759")
plot_roc_single_predictors("241_715")
plot_roc_single_predictors("282_761")
plot_roc_single_predictors("261_739")
```


```{r}
plot_roc_combined_predictors <- function(assay_id_to_plot) {
 
  test_data <- data.frame(
    response =  response %>% extract2(assay_id_to_plot), 
    result_ge_cp = result_vector_ge_cp %>% extract2(assay_id_to_plot),
    result_ge_mo_cp = result_vector_ge_mo_cp %>% extract2(assay_id_to_plot),
    result_mo_cp = result_vector_mo_cp %>% extract2(assay_id_to_plot),
    result_ge_mo = result_vector_ge_mo %>% extract2(assay_id_to_plot)
    )

  longdata <- melt_roc(test_data, "response", c("result_ge_cp", "result_ge_mo_cp","result_mo_cp","result_ge_mo"))

  ggplot(longdata, aes(d = D, m = M, color = name)) + 
    geom_roc(labels = FALSE, pointsize = 0) + 
    theme_linedraw() + 
    coord_fixed() +
    ggtitle( paste0("roc_",assay_id_to_plot,".png")   ) + 
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
      panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
    theme(text = element_text(size=16)) + 
    xlab("False Positive Fraction") +
    ylab("True Positive Fraction") 

  save_name <- paste0("roc_",assay_id_to_plot,".png")
  ggsave(paste0("../../../analysis/scaffold_based/figures/",save_name))
}
```

## show ROC curves 
```{r}
plot_roc_combined_predictors("280_759")
plot_roc_combined_predictors("241_715")
plot_roc_combined_predictors("282_761")
plot_roc_combined_predictors("261_739")
```

```{r}

plot_values_single_predictor <- function(plot_id) {
  
   
  plot_data_long <- test_data <- tibble(
      response =  response %>% extract2(plot_id), 
      result_ge_cp = result_vector_ge_cp %>% extract2(plot_id),
      result_ge_mo_cp = result_vector_ge_mo_cp %>% extract2(plot_id),
      result_mo_cp = result_vector_mo_cp %>% extract2(plot_id),
      result_ge_mo = result_vector_ge_mo %>% extract2(plot_id),
        result_cp = result_vector_cp %>% extract2(plot_id),
      result_mo = result_vector_mo %>% extract2(plot_id),
      result_ge = result_vector_ge %>% extract2(plot_id)
      ) %>% 
       mutate(response = coalesce(response, -10)) %>% 
      pivot_longer(-response, names_to = "descriptor", values_to = "value") %>% 
      mutate(descriptor=replace(descriptor, descriptor=="result_mo_cp", "CP+MO")) %>%
      mutate(descriptor=replace(descriptor, descriptor=="result_ge_mo_cp", "CP+GE+MO")) %>%
      mutate(descriptor=replace(descriptor, descriptor=="result_ge_mo", "GE+MO")) %>%
      mutate(descriptor=replace(descriptor, descriptor=="result_ge_cp", "CP+GE")) %>%
      mutate(descriptor=replace(descriptor, descriptor=="result_mo", "MO")) %>%
      mutate(descriptor=replace(descriptor, descriptor=="result_ge", "GE")) %>%
      mutate(descriptor=replace(descriptor, descriptor=="result_cp", "CP")) %>%
      group_by(descriptor) %>% 
      arrange(-value) %>% 
      mutate(number = 1 ) %>% 
      mutate(ticker = cumsum(number)) %>% 
      mutate(response_text = as.character(response)) %>% 
      mutate(response_text = replace(response_text, response_text == "1","hit")) %>% 
      mutate(response_text = replace(response_text, response_text == "0","no hit")) %>% 
      mutate(response_text = replace(response_text, response_text == "-10","reference data: not available")) %>% 
      arrange(response) %>% 
    filter(response > -1)

  ggplot(data = plot_data_long %>% filter(descriptor %in% c("CP","GE","MO")), aes(x = ticker, y = value,  color = response_text )) +
    geom_point( size = 1 ) +
    facet_wrap( ~ descriptor) +
    ylab("predicted value") +
    xlab("test compound") +
    theme_linedraw() +
    #coord_fixed() +
    scale_color_manual(values=c("red","blue","lightgray")) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
      panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(text = element_text(size=16))

}

```


```{r}

plot_values_combined_predictors <- function(plot_id) {
  

  plot_data_long <- test_data <- tibble(
      response =  response %>% extract2(plot_id), 
      result_ge_cp = result_vector_ge_cp %>% extract2(plot_id),
      result_ge_mo_cp = result_vector_ge_mo_cp %>% extract2(plot_id),
      result_mo_cp = result_vector_mo_cp %>% extract2(plot_id),
      result_ge_mo = result_vector_ge_mo %>% extract2(plot_id),
        result_cp = result_vector_cp %>% extract2(plot_id),
      result_mo = result_vector_mo %>% extract2(plot_id),
      result_ge = result_vector_ge %>% extract2(plot_id)
      ) %>% 
       mutate(response = coalesce(response, -10)) %>% 
      pivot_longer(-response, names_to = "descriptor", values_to = "value") %>% 
      mutate(descriptor=replace(descriptor, descriptor=="result_mo_cp", "CP+MO")) %>%
      mutate(descriptor=replace(descriptor, descriptor=="result_ge_mo_cp", "CP+GE+MO")) %>%
      mutate(descriptor=replace(descriptor, descriptor=="result_ge_mo", "GE+MO")) %>%
      mutate(descriptor=replace(descriptor, descriptor=="result_ge_cp", "CP+GE")) %>%
      mutate(descriptor=replace(descriptor, descriptor=="result_mo", "MO")) %>%
      mutate(descriptor=replace(descriptor, descriptor=="result_ge", "GE")) %>%
      mutate(descriptor=replace(descriptor, descriptor=="result_cp", "CP")) %>%
      group_by(descriptor) %>% 
      arrange(-value) %>% 
      mutate(number = 1 ) %>% 
      mutate(ticker = cumsum(number)) %>% 
      mutate(response_text = as.character(response)) %>% 
      mutate(response_text = replace(response_text, response_text == "1","hit")) %>% 
      mutate(response_text = replace(response_text, response_text == "0","no hit")) %>% 
      mutate(response_text = replace(response_text, response_text == "-10","reference data: not available")) %>% 
     arrange(response) %>% 
    filter(response > -1)

  
    ggplot(data = plot_data_long %>% filter(descriptor %in% c("CP+GE","CP+MO","GE+MO","CP+GE+MO")), aes(x = ticker, y = value,  color = response_text )) +
    geom_point(size = 1 ) +
    facet_wrap( ~ descriptor) + 
    ylab("predicted value") + 
    xlab("test compound") + 
    theme_linedraw() + 
    #coord_fixed() +
    scale_color_manual(values=c("red","blue","lightgray")) + 
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
      panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
    theme(text = element_text(size=16)) 
}

```


```{r}
plot_values_single_predictor("280_759")
plot_values_single_predictor("241_715")
plot_values_single_predictor("282_761")
plot_values_single_predictor("261_739")
```
```{r}
plot_values_combined_predictors("280_759")
plot_values_combined_predictors("241_715")
plot_values_combined_predictors("282_761")
plot_values_combined_predictors("261_739")
```


```{r}
result <- read_csv("../../../results/scaffold_based/chemprop/2020_07_evaluation_all_data.csv")
```

```{r}
result %>% 
  filter(assay_id %in% c("280_759","241_715","282_761","261_739")) %>% 
  group_by(assay_id) %>% 
  arrange(-auc) %>% 
  slice(1)
```

FPR = FP / (FP + TN)

recall = TP / (TP + FN)

 
 hit rate = hits / (hits + not hits )
          = TP / (TP + FP )


# Numbers that we want to calculdate: 

## Fraction of hits that we miss:
FN / (TP + FN) = FN / P 

## Hit Rate: 
Precision = TP / (TP + FP)

## Hit Rate Improvement: 
Precision / hit_rate 


hit rate 0.1
1 hit, 9 no hits 

hit rate = 0.01
tpr = 0.9 


```{r}
# helper function to catch test data without hits (only 0 or NA values)
auc_with_na <- function(response, result){
  ifelse(
    max(response >0, na.rm = TRUE) == 0,
    return(NA), 
    auc(response, result, direction = "<", levels = c(0, 1))
  )
} 
```

# load response 
```{r}
response <- read_csv('../../../analysis/scaffold_based/assay_matrix_discrete_test_old_scaff.csv')   %>% 
  select("280_759","241_715","282_761","261_739") %>% 
  print
```


# load predictions
```{r}
predictions <- read_csv('../../../results/scaffold_based/chemprop/predictions/late_fusion/max_fusion_cp_ge_mo_op_es.csv') %>% 
  select("280_759","241_715","282_761","261_739") %>% 
  rename("241_715_prediction" = "241_715") %>% 
  print

df_test <- cbind(predictions$`241_715_prediction`, response$`241_715`) %>% 
  as.data.frame() %>% 
  filter(complete.cases(.)) %>% 
  rename("response" = "V2", "prediction" = "V1" ) %>% 
  print
```

```{r}
# pr.curve defines class0 as hits / positive class 
scores_class_1 <- df_test  %>% filter(response == 0 ) %>% extract2("prediction")
scores_class_0 <- df_test  %>% filter(response == 1 ) %>% extract2("prediction")


out <- pr.curve(scores.class0 = scores_class_0, scores.class1 = scores_class_1, curve = TRUE)


hit_rate <- 0.01532138	

precision <- out$curve[,2]
hit_rate_improvement <- precision / hit_rate
recall <- out$curve[,1]
```


precision =  TP / (TP + FP)
recall =  TP / (TP + FN)
1 - recall = FN / (TP + FN)

```{r}
plot(
  y = 1 - recall, 
  x = hit_rate_improvement, 
  ylab = "fraction of missed hits",
  xlab = "increase in hit rate"
  
  )

plot(out)
```
y axis = number of hits

 |
 |
 |
 |
 ________________
  number of tested compounds