---
title: "read_chemprop_predictions"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

http://ec2-52-90-145-233.compute-1.amazonaws.com:9100/hub/login

##Input 
response <- read_csv('../../../analysis/scaffold_based/assay_matrix_discrete_test_old_scaff.csv')

result_vector_cp <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_cp_op_es.csv")  
result_vector_mo <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_mo_op_es.csv")  
result_vector_ge <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_ge_op_es.csv") 
result_vector_ge_cp <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_ge_cp_op_es.csv")  
result_vector_mo_cp <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_mo_cp_op_es.csv") 
result_vector_ge_mo <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_ge_mo.csv") 
result_vector_ge_mo_cp <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_ge_mo_cp_op_es.csv") 

## Optional output: 
  save_name <- paste0("roc_singe_descriptor_",assay_id_to_plot,".png")
  ggsave(paste0("../../../analysis/scaffold_based/",save_name))

## colors 
The color map sucks. To change it, use the line 
``` scale_color_manual(values=c("#F1C232","#6FA8DC","#93C47C")) ```
 in each plot function

```{r}
library(tidyverse)
library(magrittr)
library(ggplot2)
library(plotROC)
```
# read test data 
```{r}
# response <- read_csv('../../../analysis/scaffold_based/assay_matrix_discrete_test_old_scaff.csv')  %>%
response <- read_csv('../data/assay_matrix_discrete_test_old_scaff.csv')  %>% 
  print
```
## read assay prediction
```{r}
# result_vector_cp <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_cp_op_es.csv")  
# result_vector_mo <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_mo_op_es.csv")  
# result_vector_ge <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_ge_op_es.csv") 
# result_vector_ge_cp <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_ge_cp_op_es.csv")  
# result_vector_mo_cp <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_mo_cp_op_es.csv") 
# result_vector_ge_mo <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_ge_mo.csv") 
# result_vector_ge_mo_cp <- read_csv("../../../results/scaffold_based/chemprop/predictions/predictions_ge_mo_cp_op_es.csv")  

result_vector_cp <- read_csv("../predictions/predictions_cp_op_es.csv")  
result_vector_mo <- read_csv("../predictions/predictions_mo_op_es.csv")  
result_vector_ge <- read_csv("../predictions/predictions_ge_op_es.csv") 
result_vector_ge_cp <- read_csv("../predictions/predictions_ge_cp_op_es.csv")  
result_vector_mo_cp <- read_csv("../predictions/predictions_mo_cp_op_es.csv") 
result_vector_ge_mo <- read_csv("../predictions/predictions_ge_mo.csv") 
result_vector_ge_mo_cp <- read_csv("../predictions/predictions_ge_mo_cp_op_es.csv")  


```
# color codes 
# yellow F1C232 (chemical)
# blue 6FA8DC (gene expression) 
# green 93C47C (morphology)

```{r}

plot_roc_single_predictors <- function(assay_id_to_plot) {
 
  test_data <- data.frame(
    response =  response %>% extract2(assay_id_to_plot), 
    result_cp = result_vector_cp %>% extract2(assay_id_to_plot),
    result_mo = result_vector_mo %>% extract2(assay_id_to_plot),
    result_ge = result_vector_ge %>% extract2(assay_id_to_plot)
    )
  
  longdata <- melt_roc(test_data, "response", c("result_cp", "result_mo","result_ge"))
  
  ggplot(longdata, aes(d = D, m = M, color = name)) + 
    geom_roc(labels = FALSE, pointsize = 0) + 
    theme_linedraw() + 
    coord_fixed() +
    scale_color_manual(values=c("#F1C232","#6FA8DC","#93C47C")) + 
    ggtitle( paste0("roc_",assay_id_to_plot,".png")   ) + 
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
      panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
    theme(text = element_text(size=16)) + 
    xlab("False Positive Fraction") +
    ylab("True Positive Fraction")  + 
    theme(legend.position="none")
  
  save_name <- paste0("roc_singe_descriptor_",assay_id_to_plot,".png")
  ggsave(paste0("../figures/",save_name))
}
```

```{r}
plot_roc_single_predictors("280_759")
plot_roc_single_predictors("241_715")
plot_roc_single_predictors("282_761")
plot_roc_single_predictors("261_739")
```


```{r}
plot_roc_combined_predictors <- function(assay_id_to_plot) {
 
  test_data <- data.frame(
    response =  response %>% extract2(assay_id_to_plot), 
    result_ge_cp = result_vector_ge_cp %>% extract2(assay_id_to_plot),
    result_ge_mo_cp = result_vector_ge_mo_cp %>% extract2(assay_id_to_plot),
    result_mo_cp = result_vector_mo_cp %>% extract2(assay_id_to_plot),
    result_ge_mo = result_vector_ge_mo %>% extract2(assay_id_to_plot)
    )

  longdata <- melt_roc(test_data, "response", c("result_ge_cp", "result_ge_mo_cp","result_mo_cp","result_ge_mo"))

  ggplot(longdata, aes(d = D, m = M, color = name)) + 
    geom_roc(labels = FALSE, pointsize = 0) + 
    theme_linedraw() + 
    coord_fixed() +
    ggtitle( paste0("roc_",assay_id_to_plot,".png")   ) + 
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
      panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
    theme(text = element_text(size=16)) + 
    xlab("False Positive Fraction") +
    ylab("True Positive Fraction") 

  save_name <- paste0("roc_",assay_id_to_plot,".png")
  ggsave(paste0("../figures/",save_name))
}
```

## show ROC curves 
```{r}
plot_roc_combined_predictors("280_759")
plot_roc_combined_predictors("241_715")
plot_roc_combined_predictors("282_761")
plot_roc_combined_predictors("261_739")
```

```{r}

plot_values_single_predictor <- function(plot_id) {
  
  plot_data_long <- test_data <- tibble(
      response =  response %>% extract2(plot_id), 
      result_ge_cp = result_vector_ge_cp %>% extract2(plot_id),
      result_ge_mo_cp = result_vector_ge_mo_cp %>% extract2(plot_id),
      result_mo_cp = result_vector_mo_cp %>% extract2(plot_id),
      result_ge_mo = result_vector_ge_mo %>% extract2(plot_id),
        result_cp = result_vector_cp %>% extract2(plot_id),
      result_mo = result_vector_mo %>% extract2(plot_id),
      result_ge = result_vector_ge %>% extract2(plot_id)
      ) %>% 
       mutate(response = coalesce(response, -10)) %>% 
      pivot_longer(-response, names_to = "descriptor", values_to = "value") %>% 
      mutate(descriptor=replace(descriptor, descriptor=="result_mo_cp", "CP+MO")) %>%
      mutate(descriptor=replace(descriptor, descriptor=="result_ge_mo_cp", "CP+GE+MO")) %>%
      mutate(descriptor=replace(descriptor, descriptor=="result_ge_mo", "GE+MO")) %>%
      mutate(descriptor=replace(descriptor, descriptor=="result_ge_cp", "CP+GE")) %>%
      mutate(descriptor=replace(descriptor, descriptor=="result_mo", "MO")) %>%
      mutate(descriptor=replace(descriptor, descriptor=="result_ge", "GE")) %>%
      mutate(descriptor=replace(descriptor, descriptor=="result_cp", "CP")) %>%
      group_by(descriptor) %>% 
      arrange(-value) %>% 
      mutate(number = 1 ) %>% 
      mutate(ticker = cumsum(number)) %>% 
      mutate(response_text = as.character(response)) %>% 
      mutate(response_text = replace(response_text, response_text == "1","hit")) %>% 
      mutate(response_text = replace(response_text, response_text == "0","no hit")) %>% 
      mutate(response_text = replace(response_text, response_text == "-10","reference data: not available")) %>% 
    filter(response > -1)

  ggplot(data = plot_data_long %>% filter(descriptor %in% c("CP","GE","MO")), aes(x = ticker, y = value,  color = response_text )) +
    geom_point( size = 1 ) +
    facet_wrap( ~ descriptor) +
    ylab("predicted value") +
    xlab("test compound") +
    theme_linedraw() +
    #coord_fixed() +
    scale_color_manual(values=c("red","blue","lightgray")) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
      panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(text = element_text(size=16))
}

```


```{r}

plot_values_combined_predictors <- function(plot_id) {
  
  plot_data_long <- test_data <- tibble(
      response =  response %>% extract2(plot_id), 
      result_ge_cp = result_vector_ge_cp %>% extract2(plot_id),
      result_ge_mo_cp = result_vector_ge_mo_cp %>% extract2(plot_id),
      result_mo_cp = result_vector_mo_cp %>% extract2(plot_id),
      result_ge_mo = result_vector_ge_mo %>% extract2(plot_id),
        result_cp = result_vector_cp %>% extract2(plot_id),
      result_mo = result_vector_mo %>% extract2(plot_id),
      result_ge = result_vector_ge %>% extract2(plot_id)
      ) %>% 
       mutate(response = coalesce(response, -10)) %>% 
      pivot_longer(-response, names_to = "descriptor", values_to = "value") %>% 
      mutate(descriptor=replace(descriptor, descriptor=="result_mo_cp", "CP+MO")) %>%
      mutate(descriptor=replace(descriptor, descriptor=="result_ge_mo_cp", "CP+GE+MO")) %>%
      mutate(descriptor=replace(descriptor, descriptor=="result_ge_mo", "GE+MO")) %>%
      mutate(descriptor=replace(descriptor, descriptor=="result_ge_cp", "CP+GE")) %>%
      mutate(descriptor=replace(descriptor, descriptor=="result_mo", "MO")) %>%
      mutate(descriptor=replace(descriptor, descriptor=="result_ge", "GE")) %>%
      mutate(descriptor=replace(descriptor, descriptor=="result_cp", "CP")) %>%
      group_by(descriptor) %>% 
      arrange(-value) %>% 
      mutate(number = 1 ) %>% 
      mutate(ticker = cumsum(number)) %>% 
      mutate(response_text = as.character(response)) %>% 
      mutate(response_text = replace(response_text, response_text == "1","hit")) %>% 
      mutate(response_text = replace(response_text, response_text == "0","no hit")) %>% 
      mutate(response_text = replace(response_text, response_text == "-10","reference data: not available")) %>% 
    filter(response > -1)

  
    ggplot(data = plot_data_long %>% filter(descriptor %in% c("CP+GE","CP+MO","GE+MO","CP+GE+MO")), aes(x = ticker, y = value,  color = response_text )) +
    geom_point(size = 1 ) +
    facet_wrap( ~ descriptor) + 
    ylab("predicted value") + 
    xlab("test compound") + 
    theme_linedraw() + 
    #coord_fixed() +
    scale_color_manual(values=c("red","blue","lightgray")) + 
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
      panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
    theme(text = element_text(size=16)) 
}

```


```{r}
plot_values_single_predictor("280_759")
plot_values_single_predictor("241_715")
plot_values_single_predictor("282_761")
plot_values_single_predictor("261_739")
```
```{r}
plot_values_combined_predictors("280_759")
plot_values_combined_predictors("241_715")
plot_values_combined_predictors("282_761")
plot_values_combined_predictors("261_739")
```


```{r}
result <- read_csv("../results/2020_07_evaluation.csv")
```